\bfseries Convolution-based functions on tensor fields and tensor images

### 2022-08-24 paper/main.tex

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
%   -- another option: emulate cosmological simulations.
% - change N to N^3 in the appropriate locations; already done??
% - Understand what functions can and cannot be expressed on this model 
% - Extend it to non-linear maps (eg, by multiplications and contractions)
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? all linear translation equivariant functions can be written as convvolutions if the filters are as large as the image (simple observation)
% what about non-linear? is there a polynomial basis here? 
%  -- Define "local" functions, is there a characterization of functions that can be written as convolutions with small filters?

@@

\begin{definition}[$k$-$p$-tensors] \label{def.tensors}
We say that $v\in \mathbb R^d$ is a 1-$p$-tensor if $O(d)$ acts on $v$ via the action \eqref{eq.action}. 
If $v_i$ is a 1-$p_i$-tensor then $T:=v_{1}\otimes\ldots \otimes v_k$ is a rank-1 $k$-$p$-tensor, where $p=\sum_{i=1}^k p_i \mod 2$ and the action of $O(d)$ is defined as
\begin{align}
    g\cdot (v_{1}\otimes\ldots \otimes v_k) = (g\cdot v_1)\otimes \ldots \otimes (g\cdot v_k)
\end{align}
Higher rank $k$-$p$-tensors are defined as linear combinations of rank-1  $k$-$p$-tensors where the action of $O(d)$ is extended linearly.
\end{definition}

We note that in physics the 1-0-tensors are known as \emph{vectors}, the 1-1-tensors are \emph{pseudovectors}, the 0-0-tensors are \emph{scalars}, 0-1-tensors are \emph{pseudoscalars}, the $k$-1-tensors with $k\geq 2$ are \emph{pseudotensors}, and finally the $k$-0-tensors with $k\geq 2$ are known as \emph{tensors}.

@@

\begin{definition}[outer products of tensors]
If $a$ is a $k$-$p$-tensor and $b$ is a $k'$-$p'$-tensor, then the outer product $a\otimes b$ is a $(k+k')$-$(p+p')$-tensor with $[a\otimes b]_{i_1,\ldots,i_{k+k'}} = [a]_{i_1,\ldots,i_k}\,[b]_{i_{k+1},\ldots,i_{k+k'}}$
\end{definition}

If the next definition is going to use ``the torus'' then we should say a few words about that up-front, or above in the image definition.

\begin{definition}[geometric convolution]
Let $A$ be a $k$-$p$-tensor image on the $d$-torus with side length $N$.
Let $C$ be a $k'$-$p'$-tensor image (filter) on $[-m, m]^d$ where $2m+1<N$.
The geometric convolution $A\ast C$ is a $(k+k')$-$(p+p')$-tensor image such that
\begin{equation}
    (A\ast C)(\bar\i) = \sum_{\bar a\in[-m, m]^d} A(\bar\i - \bar a)\otimes C(\bar a) ~,
\end{equation}
where $\bar\i - \bar a$ is the translation of $\bar\i$ by $\bar a$ on the $d$-torus pixel grid $(\mathbb Z / N\mathbb Z)^d$.
\end{definition}
This definition is on the torus. If you are not in the torus just pad with zero tensors of the corresponding order and parity.

Convolutions can be followed by Kronecker contractions, Levi-Civita contractions and index permutations.
The Kronecker delta is the object with two indices such that it has the value $+1$ when the two indices have the same value, and $0$ otherwise.
Contraction of a $k$-$p$-tensor (with $k\geq 2$) with one application of the Kronecker delta returns a $(k-2)$-$p$-tensor.
Contraction of a $k$-$p$-tensor (with $k\geq 2$) with one application of the Kronecker delta returns a $(k-2)$-$p$-pseudotensor, because the contraction sums out one pair of indices.
The Levi-Civita symbol in $d\geq 2$ spatial dimensions is the object with $d$ indices (where $d$ is the spatial dimension) such that if the $d$ indices are not repeated and in an even-permutation order the value is $+1$ and if the $d$ indices are not repeated and in an odd-permutation order the value is $-1$, and it has the value $0$ in all other cases.
Contraction of a $k$-$p$-tensor (with $k\geq (d-1)$) with one application of the Levi-Civita symbol returns a $(k-d+2)$-$(p+1)$-pseudotensor, because the contraction sums over $d$ pairs of indices, and it changes the parity from even to odd or odd to even.
For one example of these contractions, the 2-tensor formed by the outer product of 1-tensors $a$ and $b$ can be contracted with the Kronecker delta to give the standard dot product $a^\top b = [a]_i\,[b]_j\,\delta_{ij}$, which is a 0-tensor or scalar.
For another example, the same 2-tensor can be contracted with the Levi-Civita symbol to give the standard cross product
$[a\times b]_k = [a]_i\,[b]_j\,\epsilon_{ijk}$, which is a pseudovector.

\begin{definition}[Kronecker contractions of tensors]
Let $a$ be a $k$-$p$-tensor in $\mathbb R^d$ with $k\geq 2$ such that $[a]_{i_1,\ldots i_k}\in \mathbb R$ for all $i_s = 1,\ldots, d$, and $s=1,\ldots, k$. We define the $(\alpha,\beta)$ Kronecker contraction of $a$ to be the $k-2$ tensor resulting from summing jointly over the indices $i_\alpha$ and $i_\beta$ where $\alpha < \beta \in\{1,\ldots, k\}$. In Einstein summation notation it would be $a_{i_1, \ldots, x, \ldots , x, \ldots, i_k}$ where the $x$s are placed in the positions $\alpha$ and $\beta$:
\begin{equation}
[a^{(\alpha,\beta)}]_{i_1,\ldots, i_{\alpha-1}, i_{\alpha+1}, \ldots, i_{\beta-1}, i_{\beta+1} , \ldots, i_k} := \sum_{x=1}^d [a]_{i_1, \ldots, i_{\alpha-1}, x, i_{\alpha+1}, \ldots, i_{\beta-1}, x, i_{\beta+1}. \ldots, i_k}
\end{equation}
\end{definition}
There are $\choose{k}{2}$ different index choices for this contraction, corresponding to all the possible index pairs among $k$ original indices.

\begin{definition}[Levi-Civita contractions of tensors]
Let $a$ be a $k$-$p$-tensor in $\mathbb R^d$ with $k\geq d-1$ such that $[a]_{i_1,\ldots i_k}\in \mathbb R$ for all $i_s = 1,\ldots, d$, and $s=1,\ldots, k$. We define the Levi-Civita contraction of $a$ to be the $(k-d+2)$-$(p+1)$-tensor resulting from taking the outer product of 
$a$ with the $d$-index Levi-Civita symbol $\epsilon_{i_1,i_2,\ldots,i_d}$ and then performing $d-1$ Kronecker contractions in which the first index is chosen from the (remaining) indices of $a$ and the second index is chosen from the (remaining) indices of the Levi-Civita symbol.
\end{definition}
There are $(d-1)!\,\choose{k}{d-1}$ different index choices for this contraction corresponding to an ordered list of $d-1$ indices chosen from among $k$ choices.

\begin{definition}[permutations of tensor indices]
Given a $k$-$p$-tensor $a\in (\mathbb R^d)^{\otimes k}$ and $\sigma\in S_k$ a permutation. We consider $a^\sigma$ the result of permuting the indices of $a$ according to $\sigma$:
\begin{equation}
    [a^\sigma]_{i_1, \ldots, i_k} := [a]_{\sigma^{-1}(i_1), \ldots, \sigma^{-1}(i_k)}
\end{equation}
\end{definition}

Define POOLING operation?

The following is not correct -- doesn't include permutations or pooling, and doesn't get the combinatorics right.

Now imagine that we want to find \emph{all} linear equivariant functions that go from an input $k$-tensor image of parity $p$ (SOLE: DO WE USE THIS CONCEPT OF PARITY PREVIOUSLY? IF NOT, IT SHOULD BE DEFINED. IT MIGHT SIMPLIFY OUR SHIT.) to an output $k'$-tensor image of parity $p'$, such that the input and output images are of the same size (both $N^d$).
Here are the linear operations (linear in the input image) that are permitted):
\begin{itemize}
\item Choose an integer $\ell$ in the range $0\leq\ell\leq k$ such that $(k'-k+2\,\ell)>0$.
  Convolve the input $k$-tensor image with a $(k'-k+2\,\ell)$-tensor invariant filter of parity $p\,p'$.
  Contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kronecker delta $\ell$ times, always choosing at least one index from the indices of the input image.
  There are $$\prod_{i=1}^{\ell}\frac{1}{\ell!}\,\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kronecker contractions.
\item Choose an integer $\ell$ in the range $0\leq\ell\leq k-d+1$ such that $(k'-k+d-2+2\,\ell)>0$.
  Convolve the input $k$-tensor image with a $(k'-k+d-2+2\,\ell)$-tensor invariant filter of parity $-p\,p'$.
  Contract the resulting $(k'+d-2+2\,\ell)$-tensor image (of parity $-p'$) with the Levi--Civita symbol.
  There are $$\left[\choose{k'+d-2+2\,\ell}{d-1}-\choose{k'-k+d-2+2\,\ell}{d-1}\right]$$ choices for this Levi--Civita contraction.
  Then contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kronecker delta $\ell$ times, always choosing one index from the indices of either the input image or of the Levi--Civita symbol.
  There are $$\prod_{i=1}^{\ell}\frac{1}{\ell!}\,\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kronecker contractions. (SOLE: IS THIS CONSISTENT WITH LANGUAGE ABOVE?)
\end{itemize}

other things that may be useful: eigenvalues

is it obvious how this contractions and permutations apply to the entire image? the same permutation, contraction should be applied to all pixels of the image.

@@

The convolution and contraction operations above defines a large class of linear functions from geometric images to geometric images. Non-linear functions can be constructed as products.

Algorithm: \newline
Construct all linear functions using the constructions from previous section. \newline
Construct all pixel-wise products across them. \newline
All linear functions of all pixel-wise products. \newline
That gives everything to second order. \newline

\begin{definition}[Products of geometric images]
Given an $N^d$-pixel $k_A$-tensor image $A$ and an $N^d$-pixel $k_B$-tensor image $B$, we can define a product $A\otimes B$, which is an $N^d$-pixel $(k_A+k_B)$-tensor image such that $(A\otimes B)(\bar\i)=A(\bar\i)\otimes B(\bar\i)$. These products can be contracted by the contraction rules above.
\end{definition}

\begin{definition}[Polynomial local geometric operator of degree $\ell$]
Given a $k$-tensor image $A$ and a set of $\ell$ $k'_j$-tensor geometric filters $C_j$, a geometric image can be formed by the degree-$\ell$ image product
\begin{equation}
    (A\ast C_1) \otimes (A\ast C_2) \otimes \cdots \otimes (A\ast C_\ell) ~. \label{monomial}
\end{equation}
This product can be subsequently contracted $r$ times to deliver a $K$-tensor geometric image with
\begin{equation}
    K = \ell\,k - 2\,r + \sum_{j=1}^\ell k'_j ~.
\end{equation}
A polynomial local geometric operator is a function that takes a $k$-tensor image $A$ and outputs the sum of $K$-tensor images constructed as contractions to order $K$ of tensor images from \eqref{monomial} with filters chosen by the user. 
\end{definition}

The geometric convolutions of \secref{sec:convolution} are local linear operators that take as input geometric images, and produce as output geometric images.
They are local in the sense that, at every pixel $\bar\i$ of the output image $(A\ast C)$, the convolution only makes use of the pixels of $A$ within a small neighborhood of of $\bar\i$.
Because tensors can be multiplied together using the outer product, and contracted according to the tensor contractions defined in \secref{sec:convolution}, it is possible, by multiplication, to construct a family of \emph{nonlinear} local geometric operators that take as input geometric images and produce as output geometric images.
This family of nonlinear local operators will be equivariant to the group $G_d$ when the linear local operators of which they are composed are equivariant.

Assembling the parts into a general, linear function.

With these definitions in hand, we can make geometric filters, take outer products, and contract to make a combinatorically large set of nonlinear geometric convolution operators on images made up of geometric objects.
But before we go nonlinear, we will go equivariant.

Assemble all the parts into an algorithm for making all possible monomials.

@@

>>>>

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
%   -- another option: emulate cosmological simulations.
% - change N to N^3 in the appropriate locations; already done??
% - Understand what functions can and cannot be expressed on this model 
% - Extend it to non-linear maps (eg, by multiplications and contractions)
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? all linear translation equivariant functions can be written as convvolutions if the filters are as large as the image (simple observation)
% what about non-linear? is there a polynomial basis here? 
%  -- Define "local" functions, is there a characterization of functions that can be written as convolutions with small filters?
% - There is a one-indexing and zero-indexing issue. Should we be consistent?
% - Some definitions begin with "given" some with "let". Should we try to be more consistent?

@@

\begin{definition}[$k$-$p$-tensors] \label{def.tensors}
We say that $v\in \mathbb R^d$ is a 1-$p$-tensor if $O(d)$ acts on $v$ via the action \eqref{eq.action}. 
If $v_i$ is a 1-$p_i$-tensor then $T:=v_{1}\otimes\ldots \otimes v_k$ is a rank-1 $k$-$p$-tensor, where $p=\sum_{i=1}^k p_i \mod 2$ and the action of $O(d)$ is defined as
\begin{align}
    g\cdot (v_{1}\otimes\ldots \otimes v_k) = (g\cdot v_1)\otimes \ldots \otimes (g\cdot v_k)
\end{align}
Higher rank $k$-$p$-tensors are defined as linear combinations of rank-1  $k$-$p$-tensors where the action of $O(d)$ is extended linearly.
\end{definition}
Typically we would make the parity $p$ be a bit (either 0 for even parity or 1 for odd parity) but in principle it can be any integer.

We note that in physics the 1-0-tensors are known as \emph{vectors}, the 1-1-tensors are known as \emph{pseudovectors}, the 0-0-tensors are known as \emph{scalars}, 0-1-tensors are known as \emph{pseudoscalars}, the $k$-1-tensors with $k\geq 2$ are known as \emph{pseudotensors}, and finally the $k$-0-tensors with $k\geq 2$ are the things that are commonly known as \emph{tensors}.

@@

\begin{definition}[outer products of tensors]
If $a$ is a $k$-$p$-tensor and $b$ is a $k'$-$p'$-tensor, then the outer product $a\otimes b$ is a $(k+k')$-$(p+p')$-tensor with $[a\otimes b]_{i_1,\ldots,i_{k+k'}} = [a]_{i_1,\ldots,i_k}\,[b]_{i_{k+1},\ldots,i_{k+k'}}$.
\end{definition}

SOLE: If the next definition is going to use ``the torus'' then we should say a few words about that up-front, or above in the image definition.

\begin{definition}[geometric convolution]
Let $A$ be a $k$-$p$-tensor image on the $d$-torus with side length $N$.
Let $C$ be a $k'$-$p'$-tensor image (filter) on $[-m, m]^d$ where $2m+1<N$.
The geometric convolution $A\ast C$ is a $(k+k')$-$(p+p')$-tensor image such that
\begin{equation}
    (A\ast C)(\bar\i) = \sum_{\bar a\in[-m, m]^d} A(\bar\i - \bar a)\otimes C(\bar a) ~,
\end{equation}
where $\bar\i - \bar a$ is the translation of $\bar\i$ by $\bar a$ on the $d$-torus pixel grid $(\mathbb Z / N\mathbb Z)^d$.
\end{definition}
This definition is on the torus. If you are not on the torus, just pad the image out with zero tensors of the corresponding order and parity.

Convolutions can be followed by Kronecker contractions, Levi-Civita contractions and index permutations.
The Kronecker delta ($\delta_{ij}$) is the object with two indices $ij$ such that it has the value $+1$ when the two indices have the same value ($i=j$), and $0$ otherwise.
Below we define the contraction of a $k$-$p$-tensor (with $k\geq 2$) with one application of the Kronecker delta, which returns a $(k-2)$-$p$-tensor.
The Levi-Civita symbol in $d\geq 2$ spatial dimensions is the object with $d$ indices (where $d$ is the spatial dimension) such that if the $d$ indices are not repeated and in an even-permutation order the value is $+1$ and if the $d$ indices are not repeated and in an odd-permutation order the value is $-1$, and it has the value $0$ in all other cases.
We define the contraction of a $k$-$p$-tensor (with $k\geq (d-1)$) with one application of the Levi-Civita symbol, which returns a $(k-d+2)$-$(p+1)$-tensor, because the contraction sums over $d$ pairs of indices, and it changes the parity from even to odd or odd to even.
For one example of these contractions, the 2-tensor formed by the outer product of 1-tensors $a$ and $b$ can be contracted with the Kronecker delta to give the standard dot product $a^\top b = [a]_i\,[b]_j\,\delta_{ij}$, which is a 0-tensor or scalar.
For another example, the same 2-tensor can be contracted with the Levi-Civita symbol to give the standard cross product
$[a\times b]_k = [a]_i\,[b]_j\,\epsilon_{ijk}$, which is a pseudovector.

\begin{definition}[Kronecker contractions of tensors and geometric images]
Let $a$ be a $k$-$p$-tensor in $\mathbb R^d$ with $k\geq 2$ such that $[a]_{i_1,\ldots i_k}\in \mathbb R$ for all $i_s = 1,\ldots, d$, and $s=1,\ldots, k$. We define the $(\alpha,\beta)$ Kronecker contraction of $a$ to be the $k-2$ tensor resulting from summing jointly over the indices $i_\alpha$ and $i_\beta$ where $\alpha < \beta \in\{1,\ldots, k\}$. In Einstein summation notation it would be $a_{i_1, \ldots, x, \ldots , x, \ldots, i_k}$ where the $x$s are placed in the positions $\alpha$ and $\beta$:
\begin{equation}
[a^{(\alpha,\beta)}]_{i_1, \ldots, i_k \backslash i_\alpha,i_\beta} := \sum_{i_\alpha=1}^d \sum_{i_\beta=1}^d [a]_{i_1, \ldots, i_\alpha,\ldots,i_\beta,\ldots, i_k}\,\delta_{i_\alpha, i_\beta}
\end{equation}
When Kronecker contraction is applied to a geometric image, the contraction is applied to every $k$-$p$-tensor in the image identically.
\end{definition}
There are $\choose{k}{2}$ different index choices for this contraction, corresponding to all the possible index pairs among $k$ original indices.

\begin{definition}[Levi-Civita contractions of tensors and geometric images]
Let $a$ be a $k$-$p$-tensor in $\mathbb R^d$ with $k\geq d-1$ such that $[a]_{i_1,\ldots i_k}\in \mathbb R$ for all $i_s = 1,\ldots, d$, and $s=1,\ldots, k$. We define the Levi-Civita contraction of $a$ to be the $(k-d+2)$-$(p+1)$-tensor resulting from taking the outer product of 
$a$ with the $d$-index Levi-Civita symbol $\epsilon_{i_1,i_2,\ldots,i_d}$ and then performing $d-1$ Kronecker contractions in which the first index is chosen from the (remaining) indices of $a$ and the second index is chosen from the (remaining) indices of the Levi-Civita symbol.
When a Levi-Civita contraction is applied to a geometric image, the contraction is applied to every $k$-$p$-tensor in the image identically.
\end{definition}
There are $(d-1)!\,\choose{k}{d-1}$ different index choices for the Levi-Civita contraction of a $k$-$p$-tensor.
These choices correspond to the choices for an ordered list of $d-1$ indices chosen from among $k$ index choices.

\begin{definition}[permutations of tensor indices]
Given a $k$-$p$-tensor $a$ and $\sigma\in S_k$ a permutation. We consider $a^\sigma$ the result of permuting the indices of $a$ according to $\sigma$:
\begin{equation}
    [a^\sigma]_{i_1, \ldots, i_k} := [a]_{\sigma^{-1}(i_1), \ldots, \sigma^{-1}(i_k)}
\end{equation}
When index permutation is applied to a geometric image, the permutation is applied to every $k$-$p$-tensor in the image identically.
\end{definition}

In addition to these contractions and index permutations that act pixel-wise in geometric images, it is possible to change the image size.
If $N$ is divisible by integer $f>1$, a geometric image of side length $N$ can be reduced in size to a geometric image of side length $N/f$ by the equivalent of convolution with a trivial $f\times f$ scalar filter (geometric filter of 0-0-tensors) operating with a stride of $f$.
Similarly a geometric image of side length $N$ can be expanded in size to a side length $f\,N$ by application of an interpolation operator with stride $1/f$.
\begin{definition}[pooling and un-pooling]
foo and bar.
\end{definition}

Now imagine that we want to find \emph{all} linear equivariant functions that go from an input $k$-$p$-tensor image of side length $N$ to an output $k'$-$p'$-tensor image of side length $N'$ (where either $N$ is divisible by $N'$, or $N'$ is divisible by $N$).
Here are the linear operations (linear in the input image) that are permitted:
\begin{enumerate}
    \item Perform a convolution and index contraction. For this step there are two qualitatively different options:
        \begin{itemize}
            \item Choose an integer $\ell$ in the range $0\leq\ell\leq k$ such that $(k'-k+2\,\ell)>0$.
              Convolve the input $k$-tensor image with a $(k'-k+2\,\ell)$-tensor invariant filter of parity $p\,p'$.
              Contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kronecker delta $\ell$ times, always choosing at least one index from the indices of the input image.
              There are $$\frac{1}{\ell!}\,\prod_{i=1}^{\ell}\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kronecker contractions.
            \item Choose an integer $\ell$ in the range $0\leq\ell\leq k-d+1$ such that $(k'-k+d-2+2\,\ell)>0$.
              Convolve the input $k$-tensor image with a $(k'-k+d-2+2\,\ell)$-tensor invariant filter of parity $-p\,p'$.
              Contract the resulting $(k'+d-2+2\,\ell)$-tensor image (of parity $-p'$) with the Levi--Civita symbol.
              There are $$(d-1)!\,\left[\choose{k'+d-2+2\,\ell}{d-1}-\choose{k'-k+d-2+2\,\ell}{d-1}\right]$$ choices for this Levi--Civita contraction.
              Then contract the resulting $(k'+2\,\ell)$-tensor image (of parity $p'$) with the Kronecker delta $\ell$ times, always choosing one index from the indices of either the input image or of the Levi--Civita symbol.
              There are $$\frac{1}{\ell!}\,\prod_{i=1}^{\ell}\left[\choose{k'+2\,i}{2}-\choose{k'-k+2\,i}{2}\right]$$ possible choices for these $\ell$ Kronecker contractions.
        \end{itemize}
    \item Perform (generally after the convolution and contraction) any index permutation you like (provided that $k'>1$).
      There are $k'!$ choices for the index permutation.
    \item Perform (generally after all the above) a pooling or unpooling step to get the image to side length $N'$.
\end{enumerate}

In principle there could also have been an \emph{eigenvalues} operator that is linear in the input and produces $d$ $0$-$p$-tensors.
But since any such operation can only reasonably be applied to $2$-$p$-tensors, and even for those, only Hermitian ones, we don't include this operation here.

@@

The convolution, contraction, index-permutation, and pooling operators above effectively span a large class of linear functions from geometric images to geometric images. Non-linear functions can be constructed as polynomials, or sums of products of linear function outputs.
Products here will be outer products (possibly followed by further geometric convolutions and contractions).

\begin{definition}[outer products of images]
Given a $k$-$p$-tensor image $A$ and a $k'$-$p'$-tensor image $B$, both of side length $N$, the outer product $A\otimes B$ of these images is a $(k+k')$-$(p+p')$-tensor image such that
\begin{equation}
    (A\otimes B)(\bar\i) = A(\bar\i)\otimes B(\bar\i) ~.
\end{equation}
That is, the outer products of geometric images are performed pixelwise.
\end{definition}

\begin{definition}[sums of images]
Given a $k$-$p$-tensor image $A$ and a $k$-$p$-tensor image $B$, both of side length $N$, the sum $A+B$ of these images is a $k$-$p$-tensor image such that
\begin{equation}
    (A+B)(\bar\i) = A(\bar\i)+B(\bar\i) ~.
\end{equation}
That is, the sums of geometric images are performed pixelwise.
\end{definition}

Now to construct all degree-2 monomials that produce a $k'$-$p'$-tensor image of side length $N'$ output from a $k$-$p$-tensor image of side length $N$ input, here are the rules:
\begin{enumerate}
    \item By the rules in \secref{sec:convolution}, construct any linear function that takes the input geometric image and outputs a geometric image of any order $k''$ and any parity $p''$ and any side length $N''$.
    \item By the rules in \secref{sec:convolution}, construct any other linear function that takes the input geometric image and outputs a geometric image of any order and any parity.
    There is no need for this second output image to be the same order or parity as the first, but it does have to have the same side length.
    \item Outer product these two images.
    \item By the rules in \secref{sec:convolution}, construct any linear function that takes this image outer product as input and produces a $k'$-$p'$-tensor image of side length $N'$ as output.
\end{enumerate}
We conjecture that these rules will generate all possible second-degree monomial functions of the input image (SOLE SUBJECT TO SOME CONDITIONS) that meet the output requirements. A polynomial function of degree 2 can be constructed by linear combinations of these second-degree monomial functions along with all the linear functions that also produce $k'$-$p'$-tensor images of side length $N'$ (plus perhaps constant images).
Higher-degree monomials and polynomials can be made out of products of lower-degree monomials, by generalization of the above.

SOLE: THIS PARAGRAPH OR THESE IDEAS GO ELSEWHERE, I THINK.
The geometric convolutions of \secref{sec:convolution} are local linear operators that take as input geometric images, and produce as output geometric images.
They are local in the sense that, at every pixel $\bar\i$ of the output image $(A\ast C)$, the convolution only makes use of the pixels of $A$ within a small neighborhood of of $\bar\i$.
Because tensors can be multiplied together using the outer product, and contracted according to the tensor contractions defined in \secref{sec:convolution}, it is possible, by multiplication, to construct a family of \emph{nonlinear} local geometric operators that take as input geometric images and produce as output geometric images.
This family of nonlinear local operators will be equivariant to the group $G_d$ when the linear local operators of which they are composed are equivariant.

@@

Introduce the discrete group. Why discrete?
